---
title: "Template"
author: "Studentnames and studentnumbers here"
date: "`r Sys.Date()`"
output: pdf_document
---

# Set-up your environment

```{r package_install, include=FALSE}
install.packages("tidyverse")
```

```{r packages}
require(tidyverse)
```

# Part 1 - Identify a Social Problem

## 1.1 Describe the Social Problem

Include the following:

-   Why is this relevant?

-   ...

## 1.2 Data Sourcing

### Load in the data

Preferably from a URL, but if not, make sure to download the data and store it in a shared location that you can load the data in from. Do not store the data in a folder you include in the Github repository!

```{r loading_data}
# cars is an example dataset included in the tidyverse package
dataset <- cars
```

### Provide a short summary of the dataset(s)

```{r}
summary(dataset)
```

In this case we see two variables, speed and distance but we miss information on what units they are in. km/hour? Or meters/second?

These are things that are usually included in the metadata of the dataset. Provide us with the information from your metadata that we need to understand your dataset of choice.

### Describe the type of variables included

Think of things like:

-   Do the variables contain health information or SES information?

-   Have they been measured by interviewing individuals or is the data coming from administrative sources?

# Part 2 - Quantifying

## 2.1 Data cleaning

Please use a separate 'R block' of code for each type of cleaning. So, e.g. one for missing values, a new one for removing unnecessary variables etc.

```{r data_cleaning}

```

## 2.2 Generate necessary variables

Variable 1

```{r gen_var1}

```

Variable 2

```{r gen_var2}

```

## 2.3 Visualize distributions and relationships

Visualize variable 1

```{r visualize_var1}

```

Visualize variable 2

```{r visualize_var2}

```

Visualize relationship between two variables

```{r visualize_relationship}

```

## 2.4 Analysis

Analyze the relationship between two variables

```{r analysis}

```

# Part 3 - Report

## 3.1 Discuss your findings

## 3.2 Provide a description of the input of each project member

# Part 4 - Reproducibility

## 4.1 Github repository link

Provide the link here: ...

## 4.2 Reference list
