---
title: "Template"
author: "Studentnames and studentnumbers here"
date: "`r Sys.Date()`"
output: pdf_document
---

# Set-up your environment

```{r package_install, include=FALSE}
install.packages("tidyverse")
```

```{r packages}
require(tidyverse)
```

# Part 1 - Identify a Social Problem

Use APA referencing throughout your document.

## 1.1 Describe the Social Problem

Include the following:

-   Why is this relevant?

-   ...

## 1.2 Data Sourcing

### Load in the data

Preferably from a URL, but if not, make sure to download the data and store it in a shared location that you can load the data in from. Do not store the data in a folder you include in the Github repository!

```{r loading_data}
dataset <- cars
```

cars is an example dataset included in the tidyverse package

### Provide a short summary of the dataset(s)

```{r}
summary(dataset)
```

In this case we see two variables, speed and distance but we miss information on what units they are in. km/hour? Or meters/second?

These are things that are usually included in the metadata of the dataset. Provide us with the information from your metadata that we need to understand your dataset of choice.

### Describe the type of variables included

Think of things like:

-   Do the variables contain health information or SES information?

-   Have they been measured by interviewing individuals or is the data coming from administrative sources?

# Part 2 - Quantifying

## 2.1 Data cleaning

Say we want to include only larger distances (above 2) in our dataset, we can filter for this.

```{r data_cleaning}
dataset <- dataset %>% filter(dist > 2)
```

Please use a separate 'R block' of code for each type of cleaning. So, e.g. one for missing values, a new one for removing unnecessary variables etc.

## 2.2 Generate necessary variables

Variable 1

```{r gen_var1}
dataset$duration <- dataset$speed / dataset$dist
```

Variable 2

```{r gen_var2}
dataset$duration <- dataset$speed / dataset$dist
```

## 2.3 Visualize distributions and relationships

This is way too simple an example, but is just meant for your understanding of the expected markdown structure.

```{r visualize_var1}
hist(dataset$duration)
```

Idem for variable 2.

```{r visualize_var2}
hist(dataset$speed)
```

Visualize relationship between two variables. Again this is way too simple an example, but is just meant for your understanding of the expected markdown structure.

```{r visualize_relationship}
cor(dataset$dist, dataset$speed)
```

## 2.4 Analysis

Analyze the relationship between two variables. Again this is way too simple an example, but is just meant for your understanding of the expected markdown structure.

```{r analysis}
glm(duration ~ speed, data = dataset) %>%
  summary()
```

# Part 3 - Report

## 3.1 Discuss your findings

See assignment hand-out for the guidelines.

## 3.2 Provide a description of the input of each project member

See assignment hand-out for the guidelines.

# Part 4 - Reproducibility

## 4.1 Github repository link

Provide the link here: ...

## 4.2 Reference list

Use APA referencing throughout your document.
