---
title: "Template"
author: "Studentnames and studentnumbers here"
date: "`r Sys.Date()`"
output: pdf_document
---

# Set-up your environment

Run this below only once!

```{r include=FALSE}
install.packages("tidyverse")
```

```{r packages needed}
require(tidyverse)
```

# Assignment part 1 - Go/no Go

## 1.1 Identify the Social Problem

### Why is this relevant?

## 1.2 Data Sourcing

### Load in the data

Preferably from a URL, but if not, make sure to download the data and store it in a shared location that you can load the data in from. Do not store the data in a folder you include in the Github repository!

```{r load in data}

```

### Provide a short summary/explanation

### Describe the type of variables included

## 1.3 Reference list

# Assignment part 2 - Quantifying

## 2.1 Data cleaning

Please use a seperate 'R block' of code for each type of cleaning. So, e.g. one for missing values, a new one for removing unnecessary variables etc.

```{r data cleaning}

```

## 2.2 Generate necessary variables

## 2.3 Visualize distributions and relationships

## 2.4 Analysis

# Assignment part 3 - Report

# Assignment part 4 - Reproducibility

## Github repository link

Provide the link here: ...
